Description of radiative transfer submodels

### 2019-09-10 analysis/paper/submodel-rtm.Rmd
Finish MS and 2S RTM code

---
title: "Submodel descriptions: Radiative transfer"
author: Alexey Shiklomanov
---

@@

>>>>

---
title: "Description of radiative transfer submodels"
author: Alexey Shiklomanov
bibliography: references.bib
---

@@

# Comparison

First, we generate some common inputs:

```{r, echo = TRUE}
ipft <- c(2, 1, 1)
L <- c(1, 1.5, 2)
p4 <- rrtm::prospect4(1.4, c(40, 60), 0.01, 0.01)
vis <- p4[(400:700) - 399, , ]
lr <- colMeans(vis[,,1])
lt <- colMeans(vis[,,2])

orient <- c(0.2, 0.25)

theta <- 15
S0_beam <- 0.8
S0_diff <- 1 - S0_beam
alb_ground <- 0.1

Then we run both models.

```{r}
ms_out <- multi_scatter(ipft, L, lr, lt, orient,
                        theta, S0_beam, S0_diff, alb_ground)
ts_out <- two_stream(ipft, L, lr, lt, orient,
                     theta, S0_beam, S0_diff, alb_ground)

plot(ms_out$light_level, type = "l")
lines(ts_out$light_level, col = 2)

plot(ms_out$light_diff_level, type = "l")
lines(ts_out$light_diff_level, col = 2)
```

# References
